Multitask matrix completion for learning protein interactions across diseases

### 2016-09-01 paper.tex
with eps figures, latex compilation

\section{Results on HIV data}
We incorporate an additional task: HIV (human immunodeficiency virus), which is quite dissimilar to our original setting involving three viruses (HIV is a retrovirus). This experiment tests how our multitask model behaves in the presence of a relatively outlier task. The interactions data has $\approx$4000 human-HIV PPI across several strains of which 1320 are non-homologous PPI. Please refer to the supplementary for the results.

This experiment particularly tests the robustness of all the multitask learning approaches by the addition of an unrelated task.
Table \ref{hivresults} shows the results.

\begin{table}[h]\caption{AUC-PR upon addition of a new task - HIV, in the 10\% setting. Note that STL and the homolog method build independent models so their AUC numbers are the same as in Table 2. Among the multitask learning methods, BSL-MTL's performance is not hurt by the addition of an unrelated task such as HIV.}
\label{hivresults}
\begin{small}
\begin{center}
%\def\arraystretch{1.2}
\begin{tabular}{c|cccc}
\toprule
& \multicolumn{4}{c}{10 \% training } \\
& \textit{Ebola} & \textit{Hep-C} & \textit{Influenza} & \textit{HIV} \\ \midrule
Homolog & 0.230$\pm$.06 & 0.178$\pm$.01 & 0.158$\pm$.01 & 0.170 $\pm$.01 \\
STL  & 0.189$\pm$.09 & 0.702$\pm$.08 & 0.286$\pm$.02  & 0.208 $\pm$.01 \\ 
Sparse+LR & 0.135 $\pm$.06 & 0.724 $\pm$.05 & 0.280 $\pm$.01 & 0.205 $\pm$.03  \\ 
BSL-MTL & \textbf{0.241} $\pm$.01 & \textbf{0.793} $\pm$.06 & \textbf{0.459} $\pm$.01 & \textbf{0.354} $\pm$.01  \\ \bottomrule
\end{tabular}
\end{center}
\end{small}
\end{table}

>>>>

\section{Results on HIV data}
We incorporate an additional task: HIV (human immunodeficiency virus), which is quite dissimilar to our original setting involving three viruses (HIV is a retrovirus). The interactions data (obtained from PHISTO and NIAID databases) has $\approx$4000 human-HIV PPI across several strains, of which 1320 PPI are non-homologous. This experiment particularly tests the robustness of the multitask learning approaches by the addition of a relatively unrelated task. Table \ref{hivresults} shows the results.

\begin{table}[h]\caption{AUC-PR upon addition of a new task - HIV, in the 10\% setting. Note that STL and the homolog method build independent models so their AUC numbers are the same as in Table 2. Among the multitask learning methods, BSL-MTL's performance is not hurt by the addition of a somewhat dissimilar task such as HIV.}
\label{hivresults}
\begin{small}
\begin{center}
%\def\arraystretch{1.2}
\begin{tabular}{c|cccc}
\toprule
& \multicolumn{4}{c}{10 \% training } \\
& \textit{Ebola} & \textit{Hep-C} & \textit{Influenza} & \textit{HIV} \\ \midrule
Homolog & 0.230$\pm$.06 & 0.178$\pm$.01 & 0.158$\pm$.01 & 0.170 $\pm$.01 \\
STL  & 0.189$\pm$.09 & 0.702$\pm$.08 & 0.286$\pm$.02  & 0.208 $\pm$.01 \\ 
Sparse+LR & 0.135 $\pm$.06 & 0.724 $\pm$.05 & 0.280 $\pm$.01 & 0.205 $\pm$.03  \\ 
BSL-MTL & \textbf{0.241} $\pm$.01 & \textbf{0.793} $\pm$.06 & \textbf{0.459} $\pm$.01 & \textbf{0.354} $\pm$.01  \\ \bottomrule
\end{tabular}
\end{center}
\end{small}
\end{table}
